---
title: "Info 201 Project"
output: html_document
---

# Introduction 

Every individual is experiencing the effects of the Coronavirus pandemic in some
way, shape, or form, just as we all bear responsibility for slowing its spread. 
Nine months of lockdown, well over a quarter of a million Americans dead, and 
millions more infected have lead to one of the largest mass casualty events in 
our history. A brutal virus that relegates individuals to their homes is the 
enemy of the small business, with tens of thousands closing in the wake of our 
economic downturn. This report will look at how the Coronavirus Pandemic has 
affected unemployment and revenue, and how that effect has been felt across the
myriad job sectors in the United States. We will be looking at which employment
sectors have been hit the hardest by the virus, and when the worst months
regarding revenue losses and jobless claims were. 

```{r setup, include = FALSE}
source("scripts/Sector_Bar_Chart.R")
source("scripts/NSA_Unemployment_Scatterplot.R")
```

## Chart 1 (Sector Bar Chart): 
``` {r average_random_sectors, echo = FALSE}
ggplot(data = average_random_sectors) +
  geom_col(
    mapping = aes(x = NAICS_SECTOR, y = AVERAGE_PERCENT),
    fill = "#FF6666"
  ) +
  labs(
    title = "Work Sector versus Percent of Businesses Affected by
             COVID-19",
    x = "Work Sector",
    y = "Average Weekly Percent of Businesses Affected"
  )
```

This chart was generated to show the relationship between a job sector and the
effect COVID-19 has had within businesses in that work sector. 

From the chart we can see that the Management and Utilities sectors were hit
the hardest with the highest average weekly percentage of businesses affected.

The chart also shows that within the 5 sectors chosen for the report, none of
them were spared from the effects of COVID-19 as all of them were affected to
a certain extent.



## Chart 2 (Unemployment Scatter Plot)
```{r unemployment_plot, echo = FALSE, warning= FALSE}
ggplot(data = non_seasonal_adjusted, aes(x = Date, y = N.S.A, group = 1)) +
  geom_line() +
  geom_point() +
  labs(title = "Initial Unemployment Claims Per Week",
       x = "Date",
       y = "NSA Unemployment Claims")
```

This chart was generated to show the relationship of Non Seasonally Adjusted
(NSA) unemployment claims per week in the United States since January 4th,
2020.

From this chart we can clearly see where the pandemic occurred, with a massive 
spike in unemployment claims that has been steadily decreasing since the initial
peak in the early pandemic. What this chart does not show are the continued
unemployment claims, the delta between these two would show the amount of 
Americans choosing to exit the workforce compared to those still searching for
employment

