---
title: "Info 201 Project"
output: html_document
---

# Introduction 


```{r setup, include = FALSE}
source("scripts/Sector_Bar_Chart.R")
```

## Chart 1 (Sector Bar Chart): 
``` {r average_random_sectors, echo = FALSE}
ggplot(data = average_random_sectors) +
  geom_col(
    mapping = aes(x = NAICS_SECTOR, y = AVERAGE_PERCENT),
    fill = "#FF6666"
  ) +
  labs(
    title = "Work Sector versus Percent of Businesses Affected by
             COVID-19",
    x = "Work Sector",
    y = "Average Weekly Percent of Businesses Affected"
  )
```

This chart was generated to show the relationship between a job sector and the
effect COVID-19 has had within businesses in that work sector. 

From the chart we can see that the Management and Utilities sectors were hit
the hardest with the highest average weekly percentage of businesses affected.

The chart also shows that within the 5 sectors chosen for the report, none of
them were spared from the effects of COVID-19 as all of them were affected to
a certain extent.