---
title: "Info 201 Project"
output: html_document
---

# Introduction 

Every individual is experiencing the effects of the Coronavirus pandemic in some 
way, shape, or form, just as we all bear responsibility for slowing its spread. 
Nine months of lockdown, well over a quarter of a million Americans dead, and 
millions more infected have lead to one of the largest mass casualty events in 
our history. A brutal virus that relegates individuals to their homes is the 
enemy of the small business, with tens of thousands closing in the wake of our 
economic downturn. This report will look at how the Coronavirus Pandemic has 
affected different job sectors, unemployment, and **contents of chart 3**.

```{r setup, include = FALSE}
source("scripts/Sector_Bar_Chart.R")
```

## Chart 1 (Sector Bar Chart): 
``` {r average_random_sectors, echo = FALSE}
ggplot(data = average_random_sectors) +
  geom_col(
    mapping = aes(x = NAICS_SECTOR, y = AVERAGE_PERCENT),
    fill = "#FF6666"
  ) +
  labs(
    title = "Work Sector versus Percent of Businesses Affected by
             COVID-19",
    x = "Work Sector",
    y = "Average Weekly Percent of Businesses Affected"
  )
```

This chart was generated to show the relationship between a job sector and the
effect COVID-19 has had within businesses in that work sector. 

From the chart we can see that the Management and Utilities sectors were hit
the hardest with the highest average weekly percentage of businesses affected.

The chart also shows that within the 5 sectors chosen for the report, none of
them were spared from the effects of COVID-19 as all of them were affected to
a certain extent.