---
title: "Info 201 Project"
output: html_document
---

# Introduction 

Every individual is experiencing the effects of the Coronavirus pandemic in some
way, shape, or form, just as we all bear responsibility for slowing its spread. 
Nine months of lockdown, well over a quarter of a million Americans dead, and 
millions more infected have lead to one of the largest mass casualty events in 
our history. A brutal virus that relegates individuals to their homes is the 
enemy of the small business, with tens of thousands closing in the wake of our 
economic downturn. This report will look at how the Coronavirus Pandemic has 
affected unemployment and revenue, and how that effect has been felt across the
myriad job sectors in the United States. We will be looking at which employment
sectors have been hit the hardest by the virus, and when the worst months
regarding revenue losses and jobless claims were. 

## Summary 

Of the **19** job sectors in our dataset, all saw revenue changes over the 
pandemic. During the beginning of the pandemic, with mandatory lockdowns and no 
stimulus bill on the horizon, both the US and global economies cratered. At its 
highest, **99.5%** of businesses within a sector were negatively affected by
COVID-19 in a week; at its lowest, a mere **0.2%** of businesses saw a negative 
revenue effect. With frequent weekly reports (the information sector has filed
**104** weekly reports since the pandemic), and a standard error of **19.13**
- we can see the devastation this pandemic has had on the United States economy.

```{r setup, include = FALSE}
source("scripts/Sector_Bar_Chart.R")
source("scripts/NSA_Unemployment_Scatterplot.R")
source("scripts/aggregate_table_sector.R")
```

## Aggregate Table
```{r echo = FALSE, results = 'asis'}
library("knitr")
kable(aggregate_table_sectors, caption = "Aggregate Table of Job Sectors")
```

## Chart 1 (Sector Bar Chart): 
``` {r average_random_sectors, echo = FALSE}
ggplot(data = average_random_sectors) +
  geom_col(
    mapping = aes(x = NAICS_SECTOR, y = AVERAGE_PERCENT),
    fill = "#FF6666"
  ) +
  labs(
    title = "Work Sector versus Percent of Businesses Affected by
             COVID-19",
    x = "Work Sector",
    y = "Average Weekly Percent of Businesses Affected"
  )
```

This chart was generated to show the relationship between a job sector and the
effect COVID-19 has had within businesses in that work sector. 

From the chart we can see that the Management and Utilities sectors were hit
the hardest with the highest average weekly percentage of businesses affected.

The chart also shows that within the 5 sectors chosen for the report, none of
them were spared from the effects of COVID-19 as all of them were affected to
a certain extent.

## Chart 2 (Sector Boxplot): 
``` {r, echo = FALSE}
ggplot(data = sectors) +
  geom_boxplot(aes(x = NAICS_SECTOR, y = ESTIMATE_PERCENTAGE,
                   fill = "orange")) +
  theme(axis.text.x = element_text(angle = 77, vjust = 0.5),
        plot.title = element_text(hjust = 0.5)) +
  labs(
    title = "Percentage Revenue Changes in Each Sector
        Week of October 04, 2020",
    x = "Sector",
    y = "Percent"
  )
```

This boxplot was generated to further explore the variance within each job 
sector as well as across each sector as a result of COVID-19 in October.

From the plot, we can see how the effect varies across the board, especially
when comparing with the median of that sector. Utilities had the largest
variance within the sector, where many businesses had high percentage of being
effected compared to the sector's median. The entire Management job sector was
affected the most with almost no outliers, high median percentage of change,
and high percentage of change for each business in the sector.

Most of other sectors seems to recover from the pandamic, with the median of 
change falling below 13 percent.

## Chart 3 (Unemployment Scatter Plot)
```{r unemployment_plot, echo = FALSE, warning= FALSE}
ggplot(data = non_seasonal_adjusted, aes(x = Date, y = N.S.A, group = 1)) +
  geom_line() +
  geom_point() +
  labs(title = "Initial Unemployment Claims Per Week",
       x = "Date",
       y = "NSA Unemployment Claims")
```

This chart was generated to show the relationship of Non Seasonally Adjusted
(NSA) unemployment claims per week in the United States since January 4th,
2020.

From this chart we can clearly see where the pandemic occurred, with a massive 
spike in unemployment claims that has been steadily decreasing since the initial
peak in the early pandemic. What this chart does not show are the continued
unemployment claims, the delta between these two would show the amount of 
Americans choosing to exit the workforce compared to those still searching for
employment

